Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-02 documentation/paper.tex
Wording fix in raw waveform section

Two different configurations were tested: one that operates strictly on the waveform with no position corrections of any kind (furthermore $DeepConv(\omega)$) and one with an additional position input on a lower layer such that it can learn to incorporate position corrections into its outputs ($DeepConvWithPos(\omega, \chi)$).

>>>>

Two different configurations were tested: one that operates strictly on the waveform with no position corrections of any kind (furthermore $DeepConv(\omega)$) and one with an additional position input on a lower layer such that it should be able to learn to incorporate position corrections into its outputs ($DeepConvWithPos(\omega, \chi)$).
